---
title: "Eksamen"
author: "Peter V. Dickmeiss"
date: '2023-01-29'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# The Order of the Elephant
# Packages I use for the project 
```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
```

```{r}
Elephant_real <- read_csv("Elephant_real.csv")
```


# I want a table that shows how many orders was given out under each monarch 
```{r}
elephant_sum_monarch <- Elephant_real %>% count(Elephant_real$reigning_monarch_of_Denmark, sort = TRUE)
```
 
# I want a table that shows how many different regions has received orders and how many they have received in total 
```{r}
elephant_sum_region <- Elephant_real %>% count(region, year_received_the_Order_of_the_Elephant, sort = TRUE)
```

# Count how many specific recipients from a region under a specific monarch in this case Frederik the 9th and for example Russia
```{r}
nrow(Elephant_real[Elephant_real$reigning_monarch_of_Denmark == 'Frederik_IX' & Elephant_real$region == 'Russia', ]) 
```

# Creating a table without Denmark by excluding all recipients from Denmark 
```{r}
elephant_without_denmark <- Elephant_real[rowSums(Elephant_real=="Denmark")==0,,drop=FALSE]
```

# Creating a table that only includes the recipients from Denmark
```{r}
elephant_only_denmark <- filter(elephant_sum_region, region == "Denmark")
```

# Creating elephant_by_king that shows how many different nationalities the specific king has awarded the order. Furthermore, I created a point graph that shows the most prevelent nationalty under each king
```{r}
elephant_by_king <- Elephant_real %>% group_by(reigning_monarch_of_Denmark, region) %>% 
  summarise(distinct_order = n_distinct(key_ID))
elephant_by_king
ggplot(data = elephant_by_king) +
  geom_point(mapping=aes(x = reigning_monarch_of_Denmark, y = distinct_order, color = region)) + ggtitle("All Recipients") + xlab("Monarch Giving the Order") + ylab("Number of Recipients")
```
# Making the same graph however this time as a "geom_line". I also changed the x axes to years instead of monarch.
```{r}
ggplot(data = elephant_sum_region) +
geom_line(mapping =aes(x = year_received_the_Order_of_the_Elephant, y = n, color = region)) + ggtitle("All Recipients") + xlab("Year Received the Order") + ylab("Number of Recipients")
```
# Creating a line graph by using my "elephant_only_denmark" table. Instead of doing it by monach I did it by year.
```{r}
ggplot(data = elephant_only_denmark) +
  geom_line(mapping = aes (x = year_received_the_Order_of_the_Elephant, y = n, color = region)) + ggtitle("Danish Recipients") + xlab("Year Received The Order of the Elephant") + ylab("Number of Recipients")
```


# I created a table that would count each recipient from each year. By using the "elephant_without_denmark" table I can get an idea of the number of foreign recipients each year.
```{r}
elephant_sum_foreign <- elephant_without_denmark %>% count(year_received_the_Order_of_the_Elephant, sort = TRUE) 
```
# Creating a line graph that shows international recipients each year and defining the y axes' border. 
```{r}
ggplot(data = elephant_sum_foreign) +
  geom_line(mapping = aes(x = year_received_the_Order_of_the_Elephant, y = n)) +
ylim(0, 20) + ggtitle("Foreign Recipients") + xlab("Year Received The Order of the Elephant") + ylab("Number of Recipients")
```

# Overlaping the two previosly created graphs, in order to get an idea of the diplomatic tendencies over time. Defining the limit of the y axes and the names of the graph.
```{r}
ggplot () +
  geom_line(data = elephant_only_denmark, mapping = aes (x = year_received_the_Order_of_the_Elephant, y = n, color = region)) +
  geom_line(data = elephant_sum_foreign, mapping = aes(x = year_received_the_Order_of_the_Elephant, y = n)) + 
  ylim(0, 40) + ggtitle("Foreign and Danish Recipients") + xlab("Year Received The Order of the Elephant") + ylab("Number of Recipients")

```
# Using "geom_smooth" on the two graphs to created the same graph as above. However the smooth graph is easier to comprehend.
```{r}
ggplot () +
  geom_smooth(data = elephant_only_denmark, mapping = aes (x = year_received_the_Order_of_the_Elephant, y = n, color = region)) +
  geom_smooth(data = elephant_sum_foreign, mapping = aes(x = year_received_the_Order_of_the_Elephant, y = n)) + ggtitle("Foreign and Danish Recipients") + xlab("Year Received The Order of the Elephant") + ylab("Number of Recipients")
```
# Creating another table this time with continents
```{r}
elephant_continent <- Elephant_real %>% count (continent, year_received_the_Order_of_the_Elephant, sort = TRUE)
```
# Doing the same process as I did before with excluding all values with "Denmark" but this time with "Europe".
```{r}
elephant_continent_without_europe <- elephant_continent[rowSums(elephant_continent=="Europe")==0,,drop=FALSE]
```

# Creating another "geom_line" graph that depicts the recipient from different ggplot(data = elephant_continent) +
```{r}
ggplot(data = elephant_continent) +
geom_line(mapping = aes(x = year_received_the_Order_of_the_Elephant, y = n,color = continent)) + ggtitle("Recipients According to Continents") + xlab("Year Received The Order of the Elephant") + ylab("Number of Recipients")
```
# Once again I'll create a line graph with the data from "elephant_continent_without_europe"
```{r}
ggplot(data = elephant_continent_without_europe) +
geom_line(mapping = aes(x = year_received_the_Order_of_the_Elephant, y = n,color = continent)) + ggtitle("Recipients Without Europe") + xlab("Year Received The Order of the Elephant") + ylab("Number of Recipients")
```


